---
title: "506hw1"
author: "Manqing Lin"
format: 
  html:
    code-fold: true
editor: visual
---

## Problem1

##a&b

```{r}
library(readr)
wine <- read_csv("~/Downloads/wine/wine.data")
View(wine)
show_col_types = FALSE
```

```{r}
library(readr)
winee <- read_csv("~/Downloads/wine/winee.names")
View(winee)
```

##c

c(1)

```{r}
newwine<-rbind(c(1,14.23,1.71,2.43,15.6,127,2.8,3.06,0.28,2.29,5.64,1.04,3.92,1065),wine)

View(newwine)

colnames(newwine)<-c("class","alcohol","malic acid","ash","alcalinity of ash", "magnesium","total phenols", "flavanoids", "nonflavanoid phenols","proanthocyanins","color intensity","hue","od280/od350","proline")
```

```{r}
##get the alcohol content data for each class of wine
c1al<-newwine$alcohol[newwine$class==1]
c2al<-newwine$alcohol[newwine$class==2]
c3al<-newwine$alcohol[newwine$class==3]

##calculate the maximum of alchol content for each class of wine
max(c1al)
max(c2al)
max(c3al)
```

The wine with the highest alcohol content belongs to class1.

c(2)

```{r}
##calculate the minimum of alchol content for each class of wine
min(c1al)
min(c2al)
min(c3al)
```

The wine with the lowest alcohol content belongs to class2.

c(3)

```{r}
##get all magnesium data
mag<-c(newwine$magnesium)
count<-0

##count the number of wine that have magnesium greater than 114
for (i in 1:178){
  if (mag[i]>114){
  count=count+1
  }
}
count

```

There are 26 kinds of wine have higher levels of magnesium.

c(4)

```{r}
##get magnesium data for each class of wine
c1mag<-newwine$magnesium[newwine$class==1]
c2mag<-newwine$magnesium[newwine$class==2]
c3mag<-newwine$magnesium[newwine$class==3]

##count the number of class 1 wine that have magnesium greater than 114
count1<-0
for (i in 1:length(c1mag)){
  if (c1mag[i]>114){
  count1=count1+1
  }
}
count1

##count the number of class 2 wine that have magnesium greater than 114
count2<-0
for (i in 1:length(c2mag)){
  if (c2mag[i]>114){
  count2=count2+1
  }
}
count2

##count the number of class 3 wine that have magnesium greater than 114
count3<-0
for (i in 1:length(c3mag)){
  if (c3mag[i]>114){
  count3=count3+1
  }
}
count3


```

For class 1 wines, there are 15 of them have higher levels of magnesium.

For class 2 wines, there are 6 of them have higher levels of magnesium.

For class 3 wines, there are 5 of them have higher levels of magnesium.

##d

```{r}
##calculate average value of each variable
meanvar<-c()

meanvar[1]<-mean(newwine$alcohol)
meanvar[2]<-mean(newwine$`malic acid`)
mean(newwine$ash)
mean(newwine$`alcalinity of ash`)
mean(newwine$magnesium)
mean(newwine$`total phenols`)
mean(newwine$flavanoids)
mean(newwine$`nonflavanoid phenols`)
mean(newwine$proanthocyanins)
mean(newwine$`color intensity`)
mean(newwine$hue)
mean(newwine$`od280/od350`)
mean(newwine$proline)
       

```

```{r}
##calculate average value of each variable for class 1 wines
mean(newwine$alcohol[newwine$class==1])
mean(newwine$`malic acid`[newwine$class==1])
mean(newwine$ash[newwine$class==1])
mean(newwine$`alcalinity of ash`[newwine$class==1])
mean(newwine$magnesium[newwine$class==1])
mean(newwine$`total phenols`[newwine$class==1])
mean(newwine$flavanoids[newwine$class==1])
mean(newwine$`nonflavanoid phenols`[newwine$class==1])
mean(newwine$proanthocyanins[newwine$class==1])
mean(newwine$`color intensity`[newwine$class==1])
mean(newwine$hue[newwine$class==1])
mean(newwine$`od280/od350`[newwine$class==1])
mean(newwine$proline[newwine$class==1])

```

```{r}
##calculate average value of each variable for class 2 wines
mean(newwine$alcohol[newwine$class==2])
mean(newwine$`malic acid`[newwine$class==2])
mean(newwine$ash[newwine$class==2])
mean(newwine$`alcalinity of ash`[newwine$class==2])
mean(newwine$magnesium[newwine$class==2])
mean(newwine$`total phenols`[newwine$class==2])
mean(newwine$flavanoids[newwine$class==2])
mean(newwine$`nonflavanoid phenols`[newwine$class==2])
mean(newwine$proanthocyanins[newwine$class==2])
mean(newwine$`color intensity`[newwine$class==2])
mean(newwine$hue[newwine$class==2])
mean(newwine$`od280/od350`[newwine$class==2])
mean(newwine$proline[newwine$class==2])

```

```{r}
##calculate average value of each variable for class 3 wines
mean(newwine$alcohol[newwine$class==3])
mean(newwine$`malic acid`[newwine$class==3])
mean(newwine$ash[newwine$class==3])
mean(newwine$`alcalinity of ash`[newwine$class==3])
mean(newwine$magnesium[newwine$class==3])
mean(newwine$`total phenols`[newwine$class==3])
mean(newwine$flavanoids[newwine$class==3])
mean(newwine$`nonflavanoid phenols`[newwine$class==3])
mean(newwine$proanthocyanins[newwine$class==3])
mean(newwine$`color intensity`[newwine$class==3])
mean(newwine$hue[newwine$class==3])
mean(newwine$`od280/od350`[newwine$class==3])
mean(newwine$proline[newwine$class==3])
```

| average  | alcohol | malic acid | ash | alcalinity of ash | magnesium | total phenols | flava | nonflava | proan | col inten | hue | OD  | proline |
|----------|---------|-------|------|----------|------------|----------|-------|----------|-------|----------|------|------|---------|
| varibale |         |            |     |                   |           |               |       |          |       |           |     |     |         |
| class    |         |            |     |                   |           |               |       |          |       |           |     |     |         |

: average value

```{r}

```

##e

```{r}
##perform t test for level of ash between class1 and class2
t.test(newwine$ash[newwine$class==1],newwine$ash[newwine$class==2])
```

Since the p value is smaller than 0.05, we reject the null hypothesis and conclude that there is a different in the level of ash between class 1 wine and class 2 wine at $\alpha=0.05$.

```{r}
##perform t test for level of ash between class1 and class3
t.test(newwine$ash[newwine$class==1],newwine$ash[newwine$class==3])
```

Since the p value is greater than 0.05, we fail to reject the null hypothesis and conclude that there is not different in the level of ash between class 1 wine and class 3 wine at $\alpha=0.05$.

```{r}
##perform t test for level of ash between class2 and class3
t.test(newwine$ash[newwine$class==2],newwine$ash[newwine$class==3])
```

Since the p value is smaller than 0.05, we reject the null hypothesis and conclude that there is a different in the level of ash between class 2 wine and class 3 wine at $\alpha=0.05$.

## Problem2

##a

```{r}
isPerfectPower<-function(n,p){
  r<-n^(1/p)
  if(r%%1==0){
    mylist<-list("isPerfect"=TRUE,"root"=p)
    return(mylist)
  }
}
```

##b

```{r}
findRootPower<-function(){
  
}

findRootPower(125)
```
